%-------------------------
% Resume in LaTeX
% Based on the user-provided ATS-friendly template style
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[scale=0.90,lf]{FiraMono}
\usepackage{contour}
\usepackage[normalem]{ulem}
\usepackage{tgheros}
\usepackage[T1]{fontenc}

\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}

\renewcommand*\familydefault{\sfdefault}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
    \bfseries \vspace{2pt} \raggedright \large
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-4pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\
      \textit{#3} & {\color{dark-grey} \small #4}\\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\color{dark-grey}\small #2}\\
    \end{tabular*}\vspace{-4pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\color{text-grey}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Eslam Tarek Nabawy} \\ \vspace{5pt}
    \small \faPhone* \hspace{2pt} \texttt{+201015683693} \hspace{1pt} $|$
    \hspace{1pt} \faEnvelope \hspace{2pt} \href{mailto:eslamtarek.dev@gmail.com}{\texttt{eslamtarek.dev@gmail.com}} \hspace{1pt} $|$
    \hspace{1pt} \faGithub \hspace{2pt} \href{https://github.com/EslamNabawy}{\texttt{github.com/EslamNabawy}} \hspace{1pt} $|$
    \hspace{1pt} \faLinkedin \hspace{2pt} \href{https://www.linkedin.com/in/eslam-tarek-nabawy/}{\texttt{linkedin.com/in/eslam-tarek-nabawy}}
    \\ \vspace{2pt}
    \small
    \faGlobe \hspace{2pt} \href{https://eslamnabawy.github.io/Nabawy-s-Portfolio-/}{\texttt{eslamnabawy.github.io/Nabawy-s-Portfolio-}} \hspace{1pt} $|$
    \hspace{1pt} \faMapMarker* \hspace{2pt}\texttt{6th October City, Egypt}
    \\ \vspace{-3pt}
\end{center}

%-----------SUMMARY-----------
\section{SUMMARY}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
    Flutter Software Engineer and Computer Science graduate with 3+ years of hands-on freelance and project experience building cross-platform mobile and desktop applications. Strong in Dart, Flutter, Firebase, REST APIs, WebRTC, Riverpod, BLoC/Cubit, Drift, Hive, Git, and n8n/LLM automation. Built real products across Android, Windows, Firebase-backed workflows, local-first desktop systems, and private peer-to-peer communication.
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{EXPERIENCE}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Self-Employed}{Nov. 2022 -- Present}
      {Freelance Software Developer}{6th October City, Egypt}
      \resumeItemListStart
        \resumeItem{Built Flutter mobile and desktop applications using Dart, Firebase, REST APIs, responsive UI, local persistence, and feature-based architecture across client and personal products.}
        \resumeItem{Integrated Firebase Auth, Firestore, Realtime Database, Firebase Storage, REST APIs, routing, and state management with BLoC/Cubit and Riverpod-style patterns.}
        \resumeItem{Delivered product workflows from requirements to release artifacts using Git/GitHub, documentation, debugging, and AI-assisted development while keeping implementation decisions explicit and reviewable.}
        \resumeItem{Created n8n and LLM API workflows using OpenAI, Claude, webhooks, conditional routing, and notifications to automate repetitive product and content operations.}
      \resumeItemListEnd

    \resumeSubheading
      {Local School \& Private Sessions}{Aug. 2023 -- Present}
      {Programming Instructor}{6th October City, Egypt}
      \resumeItemListStart
        \resumeItem{Taught programming fundamentals, OOP, algorithms, data structures, debugging, and practical software development through structured exercises.}
        \resumeItem{Mentored students through problem decomposition, implementation habits, and code-review thinking.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{PROJECTS}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{Brox} $|$ Flutter Desktop, Hive, Cubit/Bloc, GoRouter, Windows}{Offline-first operations app}
          \resumeItemListStart
            \resumeItem{Built a local-first Flutter desktop operations system for check-in, checkout, live sessions, customers, rooms, desks, reservations, kitchen inventory, finance, staff, memberships, analytics, roles, audit logs, export, restore, and app health.}
            \resumeItem{Designed the app around GoRouter shell routing, Cubit/Bloc state management, Hive CE local persistence, JSON-backed repositories, EasyLocalization, shared UI primitives, Windows release scripts, and GitHub Actions.}
            \resumeItem{Maintained production-style project structure with \textbf{531 Dart files under lib/src}, \textbf{98 Dart test files}, \textbf{520 widgets}, local schema version 3, backup/restore flows, permissions, diagnostics, and release documentation.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Rain} $|$ Flutter, WebRTC, Firebase, Drift, Riverpod}{Private P2P messenger}
          \resumeItemListStart
            \resumeItem{Built a private peer-to-peer chat app for Android and Windows with accepted friendships, WebRTC data-channel messaging, connection diagnostics, one-to-one file transfer, voice calls, and video calls.}
            \resumeItem{Separated Flutter UI, Riverpod state, Drift local persistence, Firebase Auth/Realtime Database signaling, Remote Config, session policy, and WebRTC media/data primitives across app, core, protocol, and peer packages.}
            \resumeItem{Implemented username sign-in, friend search, friend requests, blocking, call/file conflict guards, direct/relay route visibility, recovery states, and Android/Windows release artifacts.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{CampusSuit} $|$ Flutter, Firebase, REST APIs, BLoC}{Graduation project}
          \resumeItemListStart
            \resumeItem{Built onboarding, campus activities, events, profile management, live data, Firebase-backed workflows, and REST API integrations.}
            \resumeItem{Structured feature screens, state management, and data-backed UI flows so graduation-project requirements could grow without turning the UI layer into backend glue.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{AI Workflow Automation} $|$ n8n, OpenAI API, Claude API, Webhooks}{Automation pipelines}
          \resumeItemListStart
            \resumeItem{Built n8n workflows that connect OpenAI/Claude APIs, webhooks, notifications, and external services into repeatable AI automation pipelines.}
            \resumeItem{Automated data processing, AI-generated content flows, smart notifications, conditional routing, and error-aware workflow paths.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{So She Picks} $|$ Flutter, Firebase, Responsive UI}{E-commerce ordering app}
          \resumeItemListStart
            \resumeItem{Delivered responsive ordering UI, Firebase-backed order management, checkout flow, and loyalty points behavior for a mobile commerce experience.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {AEA Academy}{Oct. 2020 -- Jul. 2024}
      {Bachelor of Science in Computer Science}{6th October City, Egypt}
        \resumeItemListStart
          \resumeItem{\textbf{Coursework}: Data Structures, Algorithms, Object-Oriented Programming, Software Engineering, Database Systems, Operating Systems}
        \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------LEADERSHIP-----------
\section{LEADERSHIP}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Google Developer Student Club}{Oct. 2022 -- Oct. 2023}
      {Flutter Head}{AEA Academy}
      \resumeItemListStart
        \resumeItem{Led Flutter learning sessions, mentored beginner developers, and helped organize community technical events including NextGen and Google I/O extended activities.}
      \resumeItemListEnd

    \resumeSubheading
      {ICPC}{Jun. 2020 -- Oct. 2023}
      {Core Team Member}{Competitive Programming}
      \resumeItemListStart
        \resumeItem{Organized problem-solving contests and supported new members in algorithmic thinking and contest preparation.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{SKILLS}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Languages} {: Dart, JavaScript, Python, C++, Java, HTML, CSS}\vspace{2pt} \\
     \textbf{Mobile \& Frontend} {: Flutter, Flutter Desktop, Android, Windows desktop, responsive UI, Figma, React.js familiarity}\vspace{2pt} \\
     \textbf{Architecture} {: Riverpod, BLoC, Cubit, MVC, GoRouter, repository pattern, feature-based architecture}\vspace{2pt} \\
     \textbf{Backend \& Data} {: Firebase Auth, Realtime Database, Cloud Firestore, Firebase Storage, REST APIs, Drift, Hive, SQL, NoSQL}\vspace{2pt} \\
     \textbf{Realtime \& Automation} {: WebRTC, voice/video call flows, file transfer, n8n, OpenAI API, Claude API, LLM API integration, webhooks}\vspace{2pt} \\
     \textbf{Tools} {: Git, GitHub, GitHub Actions, CI/CD concepts, unit testing, debugging, Docker familiarity, AWS familiarity}
    }}
 \end{itemize}

%-----------LANGUAGES-----------
\section{LANGUAGES}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Arabic} {: Native} \hspace{12pt}
     \textbf{English} {: Upper-Intermediate / Professional proficiency}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
